Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-26 analysis/paper/paper.Rmd
Set seed before using random draws of model runs
line breaks for sentences in Rmd
Replace "_" with "*" for italics

_Physiological and Molecular Plant Pathology_ was the only journal to show a negative effect on the reproducibility score, the analysis was unable to detect any effect of any other journal titles.

@@

Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
Only two journals, _Plant Pathology_ and _Tropical Plant Pathology_ have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
Three had no instructions at all, _Forest Pathology_, _Phytopathologia Mediterranea_ and _Revista Mexicana de Fitopatología_, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.

@@

theme_set(theme_classic())
color_scheme_set(scheme = "gray")

>>>>

*Physiological and Molecular Plant Pathology* was the only journal to show a negative effect on the reproducibility score, the analysis was unable to detect any effect of any other journal titles.

@@

Most journals in our discipline fail to mention the availability of the computational methods to support the article as published.
Only two journals, *Plant Pathology* and *Tropical Plant Pathology* have full instructions for authors regarding both data and code deposition in repositories for sharing with readers.
Three had no instructions at all, *Forest Pathology*, *Phytopathologia Mediterranea* and *Revista Mexicana de Fitopatología*, with the remaining 16 journals having varying levels of instruction for authors to deposit data but not code.

@@

set.seed(23)
theme_set(theme_classic())
color_scheme_set(scheme = "gray")
